---
title: "Final Project Group 9"
author: "Nitin, Rachel, Annu"
date: "2022-12-03"
output: html_document
---
# Package Overview

This R package contains functions that perform logistic regression using numerical methods on a user's chosen response and predictor data. First inital weights for the optimising functrion are estimated and then coefficients($\beta$) which minimize the cost function are estimated  which contains response and predictor data and the intercept. This is done using the function logreg_optim() with following cost function-
$$
\hat{\beta}\::=\underset{\beta}{\operatorname{argmin}}\sum_{i=1}^{n}(-y_{i}\cdot\ln(p_{i})-(1-y_{i})\cdot\ln(1-p_{i}))
$$
where
$$
p_{i}\::=\frac{1}{1+exp(-x_{i}^{T}\beta)}
$$
with $y_{i}$ representing the $i^{\text{th}}$ observation of the response and $x_{i}$ representing the $i^{\text{th}}$ row of the predictors.

## How to install

```{r,warning=FALSE,message=FALSE}
#installing the package from github
library(devtools)
install_github("AU-R-Data-Science/Final-Project-group-9",force=TRUE)
library(LogReg)
```

## Let's load data and see how it works
```{r}

data=read.csv("winequality-red.csv")
data$quality=ifelse(data$quality<6,1,0)
n_feat=ncol(data)

dt = sort(sample(nrow(data), nrow(data)*.7))
train<-data[dt,]

x=as.matrix(train[,1:n_feat-1])
y=train[,n_feat]
head(x)
```

## Bootstrap Confidence intervals:

Below are the 95% and 90% confidence intervals for $\beta$ with 30 and 40 bootstraps respectively. 
```{r,warning=FALSE,message=FALSE}
#calling bootsrap function from package
library(boot)
bootstrapCI(x,y,alpha=0.05,n=30)
bootstrapCI(x,y,alpha=0.1,n=40)
```

## Logistic Curve

Below is the logistic curve of 2nd column of x variables vs. the predicted probabilities.

```{r}
#calling glm_plot function from package
glm_plot(x,y,2)
```

## The standard confusion matrix with cutoff 0.5. 

4)The resulting ``Confusion Matrix’’ (see this link) using a cut-off value for prediction at 0.5 (i.e. assign value 1 for predictions above 0.5 and value 0 for prediction below or equal to 0.5). In addition, based on this cut-off value, also output the following metrics:
* Prevalence
* Accuracy
* Sensitivity
* Specificity
* False Discovery Rate
* Diagnostic Odds Ratio

```{r,message=FALSE,warning=FALSE}
#calling suitable function from package
library(caret)
conf_matrix(x,y)
```

## The user can also see how various metric varies with different cutoff values and optimize the model according ly to best fit the needs.

```{r}
#calling function from package
metricplot(x,y,"Sensitivity")
metricplot(x,y,"Accuracy")
metricplot(x,y,"Specificity")
```

## Help ducoments for all functions in package are generated simply by using "?function" 

```{r}
#calling function from package
?metricplot
```
